Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-07-17 MSU-thesis-estee.tex
Added bills edits working on appendix figures
Rough draft. Needs a once over. Bill's edits in. Appendix content in.

% This is standard fontenc/inputenc for pdflatex
% If you use LuaLaTeX or XeLaTeX you should replace this with the fontspec package
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{overpic}
\usepackage{contour}
\usepackage{color}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{rotating}
\usepackage{mathtools}
\usepackage{appendix}
\usepackage{comment}\renewcommand{\arraystretch}{1.5}
\usepackage[version=3]{mhchem}

\graphicspath{{images/spacecharge/} {images/} {images/mccomparison/}  {images/dataAnalysis_2/} {images/dynamicrange/} {images/dataAnalysis/} {images/experiment/} {images/results/}  {images/intro/} }

>>>>

% This is standard fontenc/inputenc for pdflatex
% If you use LuaLaTeX or XeLaTeX you should replace this with the fontspec package
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{graphicx}
\usepackage{overpic}
\usepackage{contour}
\usepackage{color}
\usepackage{amsmath}
\usepackage{cleveref}
\usepackage{rotating}
\usepackage{mathtools}
\usepackage{appendix}
\usepackage{comment}\renewcommand{\arraystretch}{1.5}
\usepackage[version=3]{mhchem}

\graphicspath{{images/spacecharge/} {images/} {images/mccomparison/}  {images/dataAnalysis_2/} {images/dynamicrange/} {images/dataAnalysis/} {images/experiment/} {images/results/}  {images/intro/} {images/appendix/} }

### 2020-07-17 chapters/ch_appendix.tex
Rough draft. Needs a once over. Bill's edits in. Appendix content in.

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{clusterSpectraSn132}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the cluster cut.}
	\label{fig:clusterSpectralSn132}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{pocaSpectraSn132}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the DOCA cut.}
	\label{fig:docaSpectralSn132}
\end{figure}

@@

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{clusterSpectraSn108}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the cluster cut.}
	\label{fig:clusterSpectralSn132}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{pocaSpectraSn108}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the DOCA cut.}
	\label{fig:docaSpectralSn132}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{multSpectraSn108}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the ${}^{108}Sn$ cut.}
	\label{fig:multSpectralSn132}
\end{figure}

>>>>

A similar cut variation analysis was performed on the pion spectral ratio where each bin in Figure~\ref{fig:SRsn132} and \ref{fig:SRsn108} were plotted as a function of the cut parameter. Learning from the total pion ratio, we would not expect much dependence on the spectral ratio, since the ratio tends to cancel any systematic effects. Figure~\ref{fig:clusterSpectralSn132} shows the $\tin{132}{124}$ pion spectral ratio varying the number of cluster cut, after efficiency correction. Very little systematic dependence is observed except for the extreme limit of $N_c$ > 26 as was seen and discussed above. Figure~\ref{fig:docaSpectralSn132} shows the spectral ratio, varying the DOCA cut; no systematic dependence is observed. While we already know there are some physics considerations causing the multiplicity dependence I have shown the cut variation of the $\tin{132}{124}$ system multiplicity in Figure~\ref{fig:multSpectralSn132}, though no systematic error was attributed. In all no systematic errors were significant enough to add to the pion spectral ratio for the $\tin{132}{124}$ system.

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{clusterSpectraSn132}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the cluster cut in the $\tin{132}{124}$ system.}
	\label{fig:clusterSpectralSn132}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{pocaSpectraSn132}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the DOCA cut in the $\tin{132}{124}$ system.}
	\label{fig:docaSpectralSn132}
\end{figure}

@@

As we will see for the $\tin{108}{112}$ system, spectral pion ratio, the story is the exact same. Figure~\ref{fig:clusterSpectralSn108} shows the cluster cut variation, Figure~\ref{fig:docaSpectralSn108} shows the DOCA cut variation, and Figure~\ref{fig:multSpectralSn108} shows the $\tin{108}{112}$ system multiplicity cut variation.

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{clusterSpectraSn108}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the cluster cut in the $\tin{108}{112}$ system.}
	\label{fig:clusterSpectralSn108}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{pocaSpectraSn108}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the DOCA cut in the $\tin{108}{112}$ system}
	\label{fig:docaSpectralSn108}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{multSpectraSn108}
	\caption{The spectral pion ratio Y($\pi^+$)/Y($\pi^-$) when varying the ${}^{108}Sn$ cut.}
	\label{fig:multSpectralSn108}
\end{figure}

As with all the ratios, the double ratio also cancels systematic effects. Figure~\ref{fig:clusterDR} shows the cluster cut variation, Figure~\ref{fig:docaDR} shows the DOCA cut variation in the spectral double ratio observable. We have neglected to show the multiplicity, since we have already shown that it is derived from physics effects, and depends only on the impact parameter cut one intends to apply, not a free floating cut like the others.

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{clusterDR}
	\caption{The spectral pion double ratio  when varying the cluster cut.}
	\label{fig:clusterDR}
\end{figure}

\begin{figure}[!htb]
	\centering
    \includegraphics[width=\textwidth]{docaDR}
	\caption{The spectral pion double ratio when varying the DOCA cut.}
	\label{fig:docaDR}
\end{figure}
